MWA tied-array processing IV: Microsecond time resolution via PFB synthesis

### 2019-10-16 ipfb.tex
Started writing the introduction

\title[MWA Beamformer PFB Inversion]{MWA Beamformer PFB Inversion}

@@

\author[McSweeney et al.]{S. J. McSweeney$^1$, Author2, \dots
\affil{$^1$CIRA, Curtin University}%
}

@@

\begin{keywords}
keyword1 -- keyword2 -- keyword3 -- keyword4 -- keyword5
\end{keywords}
\end{frontmatter}

@@

Here is a citation: \citep{Harris2011}.

>>>>

\title[MWA tied-array processing IV]{MWA tied-array processing IV: Microsecond time resolution via PFB synthesis}

@@

\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, I. Morrison$^1$
\affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
\affil{$^2$CSIRO Astronomy and Space Science, PO Box 76, Epping, NSW 1710, Australia}
}

@@

\begin{keywords}
    instrumentation: interferometers -- pulsars: general -- techniques: interferometric
\end{keywords}
\end{frontmatter}

@@

The Murchison Widefield Array \citep[MWA;][]{Tingay2013} is a low-frequency ($\sim80$-$300\,$MHz) aperture array telescope situated in remote Western Australia.
Now in its second phase of development \citep[Phase II;][]{Wayth2018}, it consists of 256 `tiles' (sets of $4\times4$ cross-dipole antennas) distributed over an area roughly $5.3\,$km in diameter, 128 of which can be used at a single time to form an interferometer.
Originally conceived as an imaging telescope (which requires only the time-averaged cross-correlation products of the tiles, or `visibilities', to be retained on disk), it was subsequently augmented with the functionality to capture the raw complex voltages of each tile, known as the Voltage Capture System \citep[VCS;][]{Tremblay2015}.
This system (with its accompanying implementation, described in further detail below) has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
